\selectlanguage{english}
\chapter*{Abstract}
\markright{Abstract}
Renewable Energy has been one of the main topics that governments are directing research into. In countries, where many small rivers exist, small hydro power plants are built to generate energy. Usually, there are more than one small hydro power plant located alongside one river, mostly operated by different owners. Currently there exists no system to support power plant operators when making decisions regarding their power plant's operation. To increase the overall power generating efficiency, minimize the downtime as well as reduce the maintenance cost of all hydro power plants alongside one river a decision support system is needed.

The current thesis, investigates the possibility of introducing a centralized decision support system for several small, private and independent hydro power plants to optimize their energy output. Several Decision support system(DSS) types have been analyzed. The DSS design and development techniques were followed to implement a web-based prototype decision support system that combines the data-drive DSS and the knowledge-driven DSS properties. In addition to the DSS, a database design and implementation was proposed to save the collected sensor data from different power plants. 

The DSS highlights possibilities for avoiding events defined in an event matrix, which usually induce downtimes of the small hydro power plants. If these events can be minimized in number and duration, the overall energy production is higher. The DSS also processes rules defined by power plant operators. Following that, the operators are provided with proposed actions according to the received sensor data in the central database. Data visualization was also included in the prototype to further convince power plant operators that the DSS eventually contributes towards the power plants optimization. 

 