\selectlanguage{english}
\chapter*{Acknowledgment}
\markright{Acknowledgment}
\indent Foremost, I would like to express my sincere appreciation to my adviser, a.Univ.-Prof. Dr. Josef Küng for all the commitment shown in the elaboration of this project, the support and shared knowledge that contributed to the development of the web portal prototype. The constant efforts and time allocated in project investigation along with the wise ideas for both the technical and theoretical approaches were key elements in the successful delivery of the thesis.\\
\indent Besides my adviser, I would like to acknowledge with much appreciation Prof. Dr.Dr.h.c.mult. Bruno Buchberger that brought contribution to the thesis through his opinions and appreciations during the courses we had during this year under his guidance. The feedback offered by him was very important in correcting some features and improving the quality of the project.\\
% \indent Sincere thanks go to Brau Union and more exactly to its representatives, Mr. Nils Honetschläger and Mr. Alexander Brandl for their continuous support in the development of the practical application that accompanies this thesis. Their feedback and dedication was of great importance in the delivery of a solid mobile application that reflects the theoretical study carried on for the master studies.\\
% \indent I would like to sincerely thank to all the members of Diamond Dog company that were involved in the development of Brau Union Plus API that enforced the back-end part for the application for their advice and support in carrying on the development process. \\
\indent Furthermore, I would to like express my deepest appreciation to all the professors from Johannes Kepler University of Linz whose courses I followed for all the knowledge transmitted and for their devotion. All this knowledge stood at the foundation of constructing this thesis.\\
\indent A special gratitude I give to all the persons that inspired me throughout my professional path: teachers from high-school that believed in me, teammates from my previous job for all their help and advice as well as motivating me to peruse my postgraduate degree. \\
\indent Finally yet importantly, I would like to express my sincere thanks to my family and my friends for offering me their support during my studies and throughout life, for believing in my aims and for encouraging me in all the efforts undertaken to reach my dreams.